% ============================================================================
% CHAPTER 17: REFERENCES
% ============================================================================

\chapter{References}

\vspace{12pt}

\noindent This chapter lists all sources, references, and materials consulted during the preparation of this project management plan.

% ============================================================================
\section{Books and Textbooks}

\begin{enumerate}[leftmargin=*]
    \item Project Management Institute. (2021). \textit{A Guide to the Project Management Body of Knowledge (PMBOK Guide)} -- Seventh Edition. Project Management Institute.
    
    \item Schwalbe, K. (2019). \textit{Information Technology Project Management} (9th ed.). Cengage Learning.
    
    \item Wysocki, R. K. (2019). \textit{Effective Project Management: Traditional, Agile, Extreme, Hybrid} (8th ed.). Wiley.
    
    \item Kerzner, H. (2017). \textit{Project Management: A Systems Approach to Planning, Scheduling, and Controlling} (12th ed.). Wiley.
    
    \item Larson, E. W., \& Gray, C. F. (2021). \textit{Project Management: The Managerial Process} (8th ed.). McGraw-Hill Education.
\end{enumerate}

% ============================================================================
\section{Standards and Guidelines}

\begin{enumerate}[leftmargin=*]
    \item IEEE Std 1058-1998. (1998). \textit{IEEE Standard for Software Project Management Plans}. Institute of Electrical and Electronics Engineers.
    
    \item ISO 21500:2012. (2012). \textit{Guidance on Project Management}. International Organization for Standardization.
    
    \item ISO/IEC 12207:2017. (2017). \textit{Systems and Software Engineering – Software Life Cycle Processes}. International Organization for Standardization.
\end{enumerate}

% ============================================================================
\section{Academic Papers and Articles}

\begin{enumerate}[leftmargin=*]
    \item Atkinson, R. (1999). Project management: cost, time and quality, two best guesses and a phenomenon, its time to accept other success criteria. \textit{International Journal of Project Management}, 17(6), 337-342.
    
    \item Zwikael, O., \& Smyrk, J. (2011). Project management for the creation of organisational value. \textit{Project Management Journal}, 42(3), 13-25.
    
    \item Turner, R., \& Zolin, R. (2012). Forecasting success on large projects: Developing reliable scales to predict multiple perspectives by multiple stakeholders over multiple time frames. \textit{Project Management Journal}, 43(5), 87-99.
\end{enumerate}

% ============================================================================
\section{Online Resources and Documentation}

\begin{enumerate}[leftmargin=*]
    \item Project Management Institute. (2024). \textit{Practice Standard for Work Breakdown Structures}. Retrieved from https://www.pmi.org
    
    \item Microsoft Corporation. (2024). \textit{Microsoft Project Documentation and User Guide}. Retrieved from https://support.microsoft.com/project
    
    \item Atlassian. (2024). \textit{Agile and Project Management Best Practices}. Retrieved from https://www.atlassian.com/agile
    
    \item Smartsheet. (2024). \textit{Gantt Chart Guide and Templates}. Retrieved from https://www.smartsheet.com/gantt-chart-guide
\end{enumerate}

% ============================================================================
\section{Software and Tools}

\begin{enumerate}[leftmargin=*]
    \item Microsoft Corporation. (2024). \textit{Microsoft Project Professional 2024}. Project management and scheduling software.
    
    \item Microsoft Corporation. (2024). \textit{Microsoft Visio 2024}. Diagramming and vector graphics application.
    
    \item The LaTeX Project. (2024). \textit{LaTeX Document Preparation System}. Retrieved from https://www.latex-project.org
    
    \item Overleaf. (2024). \textit{Online LaTeX Editor}. Retrieved from https://www.overleaf.com
\end{enumerate}

% ============================================================================
\section{University and Institutional Resources}

\begin{enumerate}[leftmargin=*]
    \item [Your University Name]. (2024). \textit{Academic Calendar and Registration Policies}. Office of the Registrar.
    
    \item [Your University Name]. (2024). \textit{Information Technology Strategic Plan}. IT Department.
    
    \item [Your University Name]. (2024). \textit{Student Information System Documentation}. IT Department.
\end{enumerate}

% ============================================================================
\section{Industry Reports and White Papers}

\begin{enumerate}[leftmargin=*]
    \item Gartner, Inc. (2023). \textit{Market Guide for Higher Education Student Information Systems}. Gartner Research.
    
    \item EDUCAUSE. (2023). \textit{Key Issues in Teaching and Learning}. EDUCAUSE Center for Analysis and Research.
    
    \item Ellucian. (2023). \textit{The Future of Student Registration Systems}. Ellucian White Paper Series.
\end{enumerate}

% ============================================================================
\section{Related Projects and Case Studies}

\begin{enumerate}[leftmargin=*]
    \item University of XYZ. (2022). \textit{Implementation of Online Course Registration System: A Case Study}. Internal project documentation.
    
    \item ABC University. (2023). \textit{Lessons Learned from Student Portal Development}. Project closure report.
\end{enumerate}

% ============================================================================
\section{Financial and Cost Estimation Resources}

\begin{enumerate}[leftmargin=*]
    \item International Function Point Users Group (IFPUG). (2024). \textit{Function Point Counting Practices Manual}. Retrieved from https://www.ifpug.org
    
    \item COCOMO II. (2024). \textit{Constructive Cost Model for Software Estimation}. Retrieved from http://csse.usc.edu/csse/research/COCOMOII/cocomo\_main.html
    
    \item Central Bank of Egypt. (2024). \textit{Exchange Rates and Economic Indicators}. Retrieved from https://www.cbe.org.eg
\end{enumerate}

% ============================================================================
\section{Risk Management Resources}

\begin{enumerate}[leftmargin=*]
    \item Project Management Institute. (2019). \textit{Practice Standard for Project Risk Management}. Project Management Institute.
    
    \item Hillson, D., \& Murray-Webster, R. (2017). \textit{Understanding and Managing Risk Attitude} (2nd ed.). Routledge.
\end{enumerate}

% ============================================================================
\section{Quality Management and Testing}

\begin{enumerate}[leftmargin=*]
    \item IEEE Std 829-2008. (2008). \textit{IEEE Standard for Software and System Test Documentation}. Institute of Electrical and Electronics Engineers.
    
    \item ISO/IEC 25010:2011. (2011). \textit{Systems and Software Engineering – Systems and Software Quality Requirements and Evaluation (SQuaRE)}. International Organization for Standardization.
\end{enumerate}

% ============================================================================
\section{Additional References}

\par Additional references specific to course prerequisites, timetabling algorithms, and concurrent registration handling:

\begin{enumerate}[leftmargin=*]
    \item Burke, E. K., \& Petrovic, S. (2002). Recent research directions in automated timetabling. \textit{European Journal of Operational Research}, 140(2), 266-280.
    
    \item Schaerf, A. (1999). A survey of automated timetabling. \textit{Artificial Intelligence Review}, 13(2), 87-127.
    
    \item Gray, J., \& Reuter, A. (1992). \textit{Transaction Processing: Concepts and Techniques}. Morgan Kaufmann. (For concurrency control)
\end{enumerate}

\vspace{1cm}

\noindent \textit{Note: This reference list should be updated with actual sources used during your project preparation. Add any additional sources consulted for specific sections, diagrams, or analyses. Follow your university's preferred citation style (APA, IEEE, etc.).}
